Testing Methodologies for Asynchronous Centralized Simulations\\

### 2020-12-04 paper/PaperDraft2.tex
Paper updates

\begin{figure}[htbp]
\centerline{\includegraphics [width = 6cm, height = 9cm] {Class2.0.PNG}}
\caption{Modified Class Diagram with Testing Framework}
\end{figure}

This testing framework relies on the ability to access the internal state of any client instance of NodeTank. The reader may be interested to know that the author of NodeTank 
elected to utilize the prototype pattern, which is a JavaScript design pattern which allows for great control over inheritance while exposing any closures to outside observers[7]. For example, 
let's take the Game class from the client-side in consideration. In Fig 10. we can see that the variable "game" is defined into two sections: there is a function declaration, whose body functionally 
behaves like a constructor, and a prototype assignment, which is a set of methods inherited by all instances of game. The keen reader will note that this is not quite the same classical inheritance
mechanism utilized by languages such as Java, however we will continue to refer to them as classes as functionally they behave similarly enough.

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 5cm] {GameCodeSnippet.jpg}}
\caption{Snippet of the Game Class}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 2.8cm] {TokenTestSnippet.jpg}}
\caption{Snippet of Test Case for Requesting a Token}
\end{figure}

\begin{lstlisting}[language=JavaScript]
    let id2 = t.registerTest("testCase2");
    let test2 = (resolve, reject) => {
        t.requestToken(player1Name, (token) => {
            if (t.assertExists(token)) {
                t.passTest(id2);
                resolve ? resolve() : null;
            }
            else {
                t.failTest(id2);
                resolve ? resolve() : null;
            }
        });
    };

\end{lstlisting}

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics [width = 6cm, height = 9cm] {classv2.PNG}}
\caption{Modified Class Diagram with Testing Framework}
\end{figure}

This testing framework relies on the ability to access the internal state of any client instance of NodeTank. The reader may be interested to know that the author of NodeTank 
elected to utilize the prototype pattern, which is a JavaScript design pattern which allows for great control over inheritance while exposing any closures to outside observers[7]. For example, 
let's take the Game class from the client-side in consideration. In Listing 1, we can see that the variable "game" is defined into two sections: there is a function declaration, whose body functionally 
behaves like a constructor, and a prototype assignment, which is a set of methods inherited by all instances of game. The keen reader will note that this is not quite the same classical inheritance
mechanism utilized by languages such as Java, however we will continue to refer to them as classes as functionally they behave similarly enough.

\begin{lstlisting}[language=JavaScript,caption={Snippet of the Game Class}]
    game = function(canvas, socket, token, name) {
		this.canvas = canvas;
		this.socket = socket;
		this.token = token;
		this.name = name;
		this.initCallback = undefined;
		//...
	};

game.prototype = {
    //set up an instance of the game
    init: function(callback) {
        this.initCallback = callback;
        this.configSocket();
        console.log(this.name);
        this.socket.emit('joinGame', {
            token: this.token,
            name: this.name
        });
    },
\end{lstlisting}

@@

\begin{lstlisting}[language=JavaScript,caption={Snippet of Test Case for Requesting a Token}]
    let id2 = t.registerTest("testCase2");
    let test2 = (resolve, reject) => {
        t.requestToken(player1Name, (token) => {
            if (t.assertExists(token)) {
                t.passTest(id2);
                resolve ? resolve() : null;
            }
            else {
                t.failTest(id2);
                resolve ? resolve() : null;
            }
        });
    };
\end{lstlisting}
